Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/experiments.tex
puts captions below figures
combines references to single bib file

We compare the performance of the Algorithm 1, which is specific to the parallel problem, but does not require knowledge of $\boldsymbol{q}$, with that of Algorithm 2 and the Successive Reject algorithm of \cite{}. For each experiment, we show the average regret over 10,000 simulations with error bars displaying three standard errors.

@@

\begin{figure}[h]
\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$}
\label{fig:simple_vs_m}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_m_N50_T400_s1000_20160205_0910.pdf}
\end{figure}

@@

\begin{figure}
\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and $\epsilon = \sqrt{\frac{N}{8T}}$}
\label{fig:simple_vs_T_vary_epsilon}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_T_N50_a4_s10000_20160204_1831}
\end{figure}

\begin{figure}
\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and fixed $\epsilon = .3$}
\label{fig:simple_vs_T}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_T_N50_a4_s10000_20160205_1532}
\end{figure}

>>>>

We compare the performance of the Algorithm 1, which is specific to the parallel problem, but does not require knowledge of $\boldsymbol{q}$, with that of Algorithm 2 and the Successive Reject algorithm of \cite{audibert2010best}. For each experiment, we show the average regret over 10,000 simulations with error bars displaying three standard errors.

@@

\begin{figure}[h]
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_m_N50_T400_s1000_20160205_0910.pdf}
\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$}
\label{fig:simple_vs_m}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_T_N50_a4_s10000_20160204_1831}
\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and $\epsilon = \sqrt{\frac{N}{8T}}$}
\label{fig:simple_vs_T_vary_epsilon}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_T_N50_a4_s10000_20160205_1532}
\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and fixed $\epsilon = .3$}
\label{fig:simple_vs_T}
\end{figure}
